---
title: "RHadoop Install"
output: html_document
---
## Installation
# This script helps the user install RHadoop on Bionic Beaver. All dependencies of RHadoop, with the exception of RHbase, are successfully installed.
# Also shown are introductory scripts to run against the Hadoop cluster, the setup of which is not covered here.
```{r setup, include=FALSE}
install.packages(c("Rcpp", "RJSONIO", "bitops", "digest","functional", "stringr", "plyr", "reshape2", "dplyr","R.methodsS3", "caTools", "Hmisc"))
#.libPaths()
# set up environment variables
Sys.setenv(HADOOP_CMD="/home/user/Documents/hadoop-3.1.2/bin/hadoop")
Sys.setenv(HADOOP_CONF_DIR="/home/user/Documents/hadoop-3.1.2/etc/hadoop")
# if necessary, run export HADOOP_CONF_DIR=/home/user/Documents/hadoop-3.1.2/etc/hadoop
Sys.setenv(JAVA_HOME="/usr/lib/jvm/java-11-openjdk-amd64")
Sys.setenv(HADOOP_STREAMING="/home/user/Documents/hadoop-3.1.2/share/hadoop/tools/lib/hadoop-streaming-3.1.2.jar")
# download RHadoop packages: https://github.com/RevolutionAnalytics/RHadoop/wiki/Downloads
# run "sudo apt-get install r-cran-rjava" to install rJava since install.packages("rJava") won't work.
# if rJava fails to load in the above "run sudo R CMD javareconf"
install.packages("rJava")
# if the above fails, try sol'ns in https://stackoverflow.com/questions/42562160/r-cmd-javareconf-not-finding-jni-h
# follow these steps too if rJava fails to load: https://stackoverflow.com/questions/28462302/libjvm-so-cannot-open-shared-object-file-no-such-file-or-directory
# now install the following via terminal:
# run R CMD INSTALL rhdfs_1.0.8.tar.gz
# run R CMD INSTALL rmr2_3.3.1.tar.gz
```
## RHbase Installation
# there are numerous incompatibilities present when attempting to install rhbase, so the following code is ineffective. Skip it.
# install Thrift 0.90: https://thrift-tutorial.readthedocs.io/en/latest/installation.html via https://archive.apache.org/dist/thrift/0.9.0/
# type tar -xvzf thrift-0.9.0.tar.gz -C /home/user/Documents
# type cd Documents/thrift-0.9.0/contrib/fb303$ and then ./bootstrap.sh
# type cd and then cd Documents/thrift-0.9.0 and then ./configure
# run R CMD INSTALL rhbase_1.2.1.tar.gz```

## Installation Test
```{r test}
# test RHadoop (minus RHbase) installation by scripting objects in R and processing through Hadoop
library(rJava)
library(rhdfs)
library(rmr2)
hdfs.init() # initialize hdfs package
hdfs.defaults() # retrieve hdfs defaults
small.ints=to.dfs(1:10) # using rmr package; writes objects to file system
# define MapReduce job
mapreduce(input = small.ints,  map = function(k, v){
  lapply(seq_along(v), function(r){
  x <- runif(v[[r]])
  keyval(r,c(max(x),min(x))) })})

output <- from.dfs('/tmp/file56dfe473d0d')
View(output)
table_output <- do.call('rbind', lapply(output$val,"[[",2))
table_output # produces NULL
```
